---
title: "Anime Data"
author: "John Collopy"
date: "9/21/2023"
output: html_document
---

### Introduction:

The goal of our project is to build build an anime recommendation system. This project is inspired by the popularity of anime media, hence, we want to create a tool that would allow users to input in a series of anime titles they enjoyed and then receive a collection of new anime titles they may enjoy.

### Step 1: Data Collection

Our dataset can be found [here](https://www.kaggle.com/datasets/hernan4444/anime-recommendation-database-2020) on Kaggle. We chose to use this dataset because it contains exhaustive information about a large collection of anime entertainment.

Here is the list of features contained in the dataset:

1. MAL_ID: MyAnimelist ID of the anime. (e.g. 1)
2. Name: full name of the anime. (e.g. Cowboy Bebop)
3. Score: average score of the anime given from all users in MyAnimelist database. (e.g. 8.78)
4. Genres: comma separated list of genres for this anime. (e.g. Action, Adventure, Comedy, Drama, Sci-Fi, Space)
5. English name: full name in english of the anime. (e.g. Cowboy Bebop)
6. Japanese name: full name in japanses of the anime. (e.g. カウボーイビバップ)
7. Type: TV, movie, OVA, etc. (e.g. TV)
8. Episodes': number of chapters. (e.g. 26)
9. Aired: broadcast date. (e.g. Apr 3, 1998 to Apr 24, 1999)
10. Premiered: season premiere. (e.g. Spring 1998)
11. Producers: comma separated list of produducers (e.g. Bandai Visual)
12. Licensors: comma separated list of licensors (e.g. Funimation, Bandai Entertainment)
13. Studios: comma separated list of studios (e.g. Sunrise)
14. Source: Manga, Light novel, Book, etc. (e.g Original)
15. Duration: duration of the anime per episode (e.g 24 min. per ep.)
16. Rating: age rate (e.g. R - 17+ (violence & profanity))
17. Ranked: position based in the score. (e.g 28)
18. Popularity: position based in the the number of users who have added the anime to their list. (e.g 39)
19. Members: number of community members that are in this anime's "group". (e.g. 1251960)
20. Favorites: number of users who have the anime as "favorites". (e.g. 61,971)
21. Watching: number of users who are watching the anime. (e.g. 105808)
22. Completed: number of users who have complete the anime. (e.g. 718161)
23. On-Hold: number of users who have the anime on Hold. (e.g. 71513)
24. Dropped: number of users who have dropped the anime. (e.g. 26678)
25. Plan to Watch': number of users who plan to watch the anime. (e.g. 329800)
26. Score-10': number of users who scored 10. (e.g. 229170)
27. Score-9': number of users who scored 9. (e.g. 182126)
28. Score-8': number of users who scored 8. (e.g. 131625)
29. Score-7': number of users who scored 7. (e.g. 62330)
30. Score-6': number of users who scored 6. (e.g. 20688)
31. Score-5': number of users who scored 5. (e.g. 8904)
32. Score-4': number of users who scored 4. (e.g. 3184)
33. Score-3': number of users who scored 3. (e.g. 1357)
34. Score-2': number of users who scored 2. (e.g. 741)
35. Score-1': number of users who scored 1. (e.g. 1580)

This dataset is limited in some regards, largely because it contains animes made exclusively before 2020. That being said, it still contains information about 17.562 anime and the preference from 325.772 different users, as well as relevant features, and so we believe this dataset will allow us to create an effective recommendation tool.

Below: we import the necessary libraries,upload the dataset, and view the first 5 rows.

```{r}
# Importing the necessary libraries and data
library(tidyverse)
anime <- read.csv("anime.csv")
head(anime)
```

### Step 2: ETL

Our data now needs to be prepared for modeling. Firstly, it is important to check if there are any null or missing values in the data frame.

```{r}
null_values <- is.na(anime)
null_counts <- colSums(null_values)
null_counts
```


Since there are no null values, the data frame can be prepped for modeling. The first column to amend is the "Genres" column. First, let's look at the column.

```{r}
head(anime$Genres)
```

Next, let's check what type of data is in the column.

```{r}
typeof(anime$Genres)
```

Next, let's check how many times each genre appears in the column.

```{r}
genre_counts <- anime %>%
  separate_rows(Genres, sep = ", ") %>%
  group_by(Genres) %>%
  summarize(count = n()) %>%
  arrange(desc(count))

print(genre_counts)
```

For our project, we want to remove entertainment that includes explicit content and whose genre is unknown, so we create a new data frame without the undesired entertainment.

```{r}
# Removing non-family friendly content
unclean <- c("Hentai", "Ecchi", "Harem", "Yaoi", "Yuri", "Unknown")
anime_clean <- anime[ !grepl(paste(unclean, collapse="|"), anime$Genres),]
```

Now, we can re-check the counts.

```{r}
genre_counts_1 <- anime_clean %>%
  separate_rows(Genres, sep = ", ") %>%
  group_by(Genres) %>%
  summarize(count = n())%>%
  arrange(desc(count))

# Display the result
print(genre_counts_1)
```

Now, we can create Dummy Variables for the "Genres" column.
```{r}  
# Creating Dummy Variables For Genre
anime_clean <- anime_clean %>%
  mutate(Genres = strsplit(Genres, ", ")) %>%
  unnest(Genres) %>%
  distinct() %>%
  mutate(dummy = 1) %>%
  spread(Genres, dummy, fill = 0)

head(anime_clean)
```

Now, we evaluate the "Rating" column. First, let's check for each rating that appears.
```{r}
unique(anime_clean$Rating)
```

Since we do not want explicit content nor content we do not know much about, we remove such entertainment.
```{r}
# Removing shows containing nudity
undesired <- c("Mild Nudity", "Unknown")
anime_clean <- anime_clean[ !grepl(paste(undesired, collapse="|"), anime_clean$Rating),]
unique(anime_clean$Rating)
```

Now, we can create Dummy Variables for "Rating".
```{r}
dummy_variables <- model.matrix(~ Rating - 1, data = anime_clean)

# Combine the dummy variables with the original data frame
anime_clean <- cbind(anime_clean, dummy_variables)

# Print the result
head(anime_clean)
```

Now, we evaluate the "Type" column. First, let's check for each rating that appears.
```{r}
unique(anime_clean$Type)
```

We remove entertainment with an unknown Type.

```{r}
anime_clean <- anime_clean[ !grepl(paste("Unknown", collapse="|"), anime_clean$Type),]
unique(anime_clean$Type)
```

Now, we can create Dummy Variables for Type.

```{r}
dummy_variables <- model.matrix(~ Type - 1, data = anime_clean)

# Combine the dummy variables with the original data frame
anime_clean <- cbind(anime_clean, dummy_variables)

# Print the result
head(anime_clean)
```

Next, we check the dates that all of the animes aired. First, we take a look at the column.

```{r}
head(anime_clean$Aired)
```

Next, we extract the year that the anime aired.

```{r}
# Extracting the year the anime aired
after_comma <- sub(".*,", "", anime_clean$Aired)
anime_clean$Year_Premiered <- substr(after_comma, 1, 5)
unique(anime_clean$Year_Premiered)
```

Next, we remove all shows that do not have a known air date.

```{r}
anime_clean <- anime_clean[ !grepl(paste("Unkno", collapse="|"), anime_clean$Year_Premiered),]
unique(anime_clean$Year_Premiered)
```

Next, we make the column the correct type.

```{r}
anime_clean$Year_Premiered <- as.factor(anime_clean$Year_Premiered)
```

Next, we check the "Source" column.

```{r}
unique(anime_clean$Source)
```

Then, we remove shows that do not have a known source.

```{r}
anime_clean <- anime_clean[ !grepl(paste("Unknown", collapse="|"), anime_clean$Source),]
unique(anime_clean$Source)
```

Then, we create Dummy Variables

```{r}
dummy_variables <- model.matrix(~ Source - 1, data = anime_clean)

# Combine the dummy variables with the original data frame
anime_clean <- cbind(anime_clean, dummy_variables)

# Print the result
print(anime_clean)
```

Next, we check the "Score" column.

```{r}
unique(anime_clean$Score)
```

```{r}
anime_clean <- anime_clean[ !grepl(paste("Unknown", collapse="|"), anime_clean$Score),]
```

```{r}
anime_clean$Score <- as.numeric(anime_clean$Score)
```

Next, we create the data frame that we will use for our modelling.

```{r}
colnames(anime_clean)
```

### Step 3: Data Visualization

We will use this section to create figures that will provide insight into our data. In order to do so, we will use the ggplot2 library. 

```{r}
library(ggplot2)
```

First, let's look at the number of animes made over time.

```{r}
year_freq <- anime_clean %>%
  group_by(Year_Premiered) %>%
  summarize(Count = n())

ggplot(year_freq, aes(x = Year_Premiered, y = Count, fill = Count)) + 
  geom_col() +
  labs(title = "Amount of Content Produced Across Years", x = "Year Premiered", y = "Count") +
  scale_fill_viridis_b()
  theme_minimal()
```

Unsurprisingly, animes have become very popular over time, particularly at the start of the 20th century. Next, let's see if the quality of anime has improved over time.

```{r}
ggplot(anime_clean, aes(x = Year_Premiered, y = Score)) +
  geom_point(stat = "summary", fun = mean, color = "blue") +
  labs(title = "Average Score Over Time",
       x = "Year Premiered",
       y = "Average Score") +
  theme_minimal()
```

The chart above suggests a positive relationship between Mean Score and Year. This would suggest that viewers like modern animes more than older animes.

Next, we shall check how often each Type appears in our data set.

```{r}
type_freq <- anime_clean %>%
  group_by(Type) %>%
  summarize(count = n())

type_freq
```

Then, we shall check how often each Rating appears in our data set.

```{r}
type_rating <- anime_clean %>%
  group_by(Rating) %>%
  summarize(count = n())

type_rating
```

Then, we can check the distribution of Score for each Type.

```{r}
ggplot(anime_clean, aes(Type, Score)) + 
  geom_boxplot(aes(fill = Type))  +
  stat_summary(fun = "mean", geom = "text", aes(label = round(..y.., 2)),
               vjust = -1, color = "Black", size = 3) +
  labs(title = "Distribution of Scores for Each Type of Media")
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

As we can see in the box-plot, TV shows earn the highest mean score. Also, none of the distributions appear to have a terribly strong skew. Additionally, the outliers almost exclusively exist below the mean, indicating that there are more terrible shows than outstanding ones.

Lastly, we can check for the distribution of scores for each Rating.

```{r}
ggplot(anime_clean, aes(Rating, Score)) + 
  geom_boxplot(aes(fill = Rating)) +
  stat_summary(fun = "mean", geom = "text", aes(label = round(..y.., 2)),
               vjust = -1, color = "Black", size = 3) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

As we can see in the box-plot, as content increases in maturity, the mean score increases. The scores for each type seem to have mild skewness, but nothing grievous. 

### Part 4: Modeling

Below, we create the dataset with all columns necessary for building the model.
```{r}
# Creating the dataset for modeling
model_data <- anime_clean %>%
  select(-c(5:34))
head(model_data)
```

```{r}
# Saving the data
write_csv(model_data, "model_data.csv")
```
