---
title: "Anime Data"
author: "John Collopy"
date: "9/21/2023"
output: html_document
---

Introduction:


Step 1: Data Collection

Our dataset can be found [here](https://www.kaggle.com/datasets/hernan4444/anime-recommendation-database-2020) on Kaggle. We chose to use this dataset because it contains exhaustive information about a large collection of anime entertainment.

Here is the list of features contained in the dataset:

1. MAL_ID: MyAnimelist ID of the anime. (e.g. 1)
2. Name: full name of the anime. (e.g. Cowboy Bebop)
3. Score: average score of the anime given from all users in MyAnimelist database. (e.g. 8.78)
4. Genres: comma separated list of genres for this anime. (e.g. Action, Adventure, Comedy, Drama, Sci-Fi, Space)
5. English name: full name in english of the anime. (e.g. Cowboy Bebop)
6. Japanese name: full name in japanses of the anime. (e.g. カウボーイビバップ)
7. Type: TV, movie, OVA, etc. (e.g. TV)
8. Episodes': number of chapters. (e.g. 26)
9. Aired: broadcast date. (e.g. Apr 3, 1998 to Apr 24, 1999)
10. Premiered: season premiere. (e.g. Spring 1998)
11. Producers: comma separated list of produducers (e.g. Bandai Visual)
12. Licensors: comma separated list of licensors (e.g. Funimation, Bandai Entertainment)
13. Studios: comma separated list of studios (e.g. Sunrise)
14. Source: Manga, Light novel, Book, etc. (e.g Original)
15. Duration: duration of the anime per episode (e.g 24 min. per ep.)
16. Rating: age rate (e.g. R - 17+ (violence & profanity))
17. Ranked: position based in the score. (e.g 28)
18. Popularity: position based in the the number of users who have added the anime to their list. (e.g 39)
19. Members: number of community members that are in this anime's "group". (e.g. 1251960)
20. Favorites: number of users who have the anime as "favorites". (e.g. 61,971)
21. Watching: number of users who are watching the anime. (e.g. 105808)
22. Completed: number of users who have complete the anime. (e.g. 718161)
23. On-Hold: number of users who have the anime on Hold. (e.g. 71513)
24. Dropped: number of users who have dropped the anime. (e.g. 26678)
25. Plan to Watch': number of users who plan to watch the anime. (e.g. 329800)
26. Score-10': number of users who scored 10. (e.g. 229170)
27. Score-9': number of users who scored 9. (e.g. 182126)
28. Score-8': number of users who scored 8. (e.g. 131625)
29. Score-7': number of users who scored 7. (e.g. 62330)
30. Score-6': number of users who scored 6. (e.g. 20688)
31. Score-5': number of users who scored 5. (e.g. 8904)
32. Score-4': number of users who scored 4. (e.g. 3184)
33. Score-3': number of users who scored 3. (e.g. 1357)
34. Score-2': number of users who scored 2. (e.g. 741)
35. Score-1': number of users who scored 1. (e.g. 1580)

Below: we import the necessary libraries,upload the dataset, and view the first 5 rows.

```{r}
# Importing the necessary libraries
library(tidyverse)
install.packages("stringi")
library(stringi)
install.packages("stringdist")
library(stringdist)
```

```{r}
# Importing the data
anime <- read.csv("anime.csv")
anime
```

Step 2: ETL

Our data now needs to be prepared for modeling. Firstly, it is important to check if there are any null or missing values in the data frame.

```{r}
null_values <- is.na(anime)
null_counts <- colSums(null_values)
null_counts
```


Since there are no null values, the data frame can be prepped for modelling. The first column to amend is the "Genres" column. First, let's look at the column.

```{r}
head(anime$Genres)
```

Next, let's check what type of data is in the column.

```{r}
typeof(anime$Genres)
```

Next, let's check how many times each genre appears in the column.

```{r}
genre_counts <- anime %>%
  separate_rows(Genres, sep = ", ") %>%
  group_by(Genres) %>%
  summarize(count = n()) %>%
  arrange(desc(count))

print(genre_counts)
```


For our project, we want to remove entertainment that includes explicit content and whose genre is unknown, so we create a new data frame without the undesired entertainment.

```{r}
# Removing non-family friendly content
unclean <- c("Hentai", "Ecchi", "Harem", "Yaoi", "Yuri", "Unknown")
anime_clean <- anime[ !grepl(paste(unclean, collapse="|"), anime$Genres),]
```

Now, we can check
```{r}
genre_counts_1 <- anime_clean %>%
  separate_rows(Genres, sep = ", ") %>%
  group_by(Genres) %>%
  summarize(count = n())%>%
  arrange(desc(count))

# Display the result
print(genre_counts_1)
```
Now, we can create Dummy Variables for the "Genres" column.
```{r}  
# Creating Dummy Variables For Genre
anime_clean <- anime_clean %>%
  mutate(Genres = strsplit(Genres, ", ")) %>%
  unnest(Genres) %>%
  distinct() %>%
  mutate(dummy = 1) %>%
  spread(Genres, dummy, fill = 0)

head(anime_clean)
```

Now, we evaluate the "Rating" column. First, let's check for each rating that appears.
```{r}
unique(anime_clean$Rating)
```

Since we do not want explicit content nor content we do not know much about, we remove such entertainment.
```{r}
# Removing shows containing nudity
undesired <- c("Mild Nudity", "Unknown")
anime_clean <- anime_clean[ !grepl(paste(undesired, collapse="|"), anime_clean$Rating),]
unique(anime_clean$Rating)
```

Now, we can create Dummy Variables for Rating.
```{r}
dummy_variables <- model.matrix(~ Rating - 1, data = anime_clean)

# Combine the dummy variables with the original data frame
anime_clean <- cbind(anime_clean, dummy_variables)

# Print the result
head(anime_clean)
```

Now, we evaluate the "Type" column. First, let's check for each rating that appears.
```{r}
unique(anime_clean$Type)
```

We remove entertainment with an unknown Type.
```{r}
anime_clean <- anime_clean[ !grepl(paste("Unknown", collapse="|"), anime_clean$Type),]
unique(anime_clean$Type)
```

Now, we can create Dummy Variables for Type.
```{r}
dummy_variables <- model.matrix(~ Type - 1, data = anime_clean)

# Combine the dummy variables with the original data frame
anime_clean <- cbind(anime_clean, dummy_variables)

# Print the result
head(anime_clean)
```

Next, we check the dates that all of the animes aired. First, we take a look at the column.

```{r}
head(anime_clean$Aired)
```

Next, we extract the year that the anime aired.

```{r}
# Extracting the year the anime aired
after_comma <- sub(".*,", "", anime_clean$Aired)
anime_clean$Year_Premiered <- substr(after_comma, 1, 5)
unique(anime_clean$Year_Premiered)
```

Next, we remove all shows that do not have a known air date.

```{r}
anime_clean <- anime_clean[ !grepl(paste("Unkno", collapse="|"), anime_clean$Year_Premiered),]
unique(anime_clean$Year_Premiered)
```

Next, we make the column numeric.

```{r}
anime_clean$Year_Premiered <- as.numeric(anime_clean$Year_Premiered)
```

Next, we check the "Source" column.

```{r}
unique(anime_clean$Source)
```

Then, we remove shows that do not have a known source.

```{r}
anime_clean <- anime_clean[ !grepl(paste("Unknown", collapse="|"), anime_clean$Source),]
unique(anime_clean$Source)
```

Then, we create Dummy Variables
```{r}
dummy_variables <- model.matrix(~ Source - 1, data = anime_clean)

# Combine the dummy variables with the original data frame
anime_clean <- cbind(anime_clean, dummy_variables)

# Print the result
print(anime_clean)
```

Next, we check the "Score" column.

```{r}
unique(anime_clean$Score)
```

```{r}
anime_clean <- anime_clean[ !grepl(paste("Unknown", collapse="|"), anime_clean$Score),]
```

```{r}
anime_clean$Score <- as.numeric(anime_clean$Score)
```

Next, we create the data frame that we will use for our modelling.

```{r}
colnames(anime_clean)
```

Step 3: Data Visualization

We will use this section to create figures that will provide insight into our data. In order to do so, we will use the ggplot2 library. 

```{r}
library(ggplot2)
```

```{r}
ggplot(anime_clean, aes(x = Year_Premiered)) +
  geom_bar() +
  labs(title = "Frequency of Each Year Premiered",
       x = "Year Premiered",
       y = "Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
```

Next, we shall check how often each Type appears in our data set.

```{r}
# Creating the barplot
ggplot(anime_clean, aes(x = Type)) +
  geom_bar() +
  labs(title = "Frequency of Each Type",
       x = "Type of Anime",
       y = "Frequency")
```

Then, we shall check how often each Rating appears in our data set.
```{r}
# Creating the barplot

ggplot(anime_clean, aes(x = Rating)) +
  geom_bar() +
  labs(title = "Frequency of Each Rating",
       x = "Rating",
       y = "Frequency")
```

```{r}
average_ratings_type <- anime_clean %>%
  group_by(Type) %>%
  summarize(mean_rating = mean(Score))

ggplot(anime_clean, aes(x = Type, y = as.numeric(Score))) +
  stat_summary(fun = "mean", geom = "col") +
  geom_text(data = average_ratings_type, aes(label = sprintf("%.2f", mean_rating), y = mean_rating + 0.1), vjust = -0.5) +
  scale_y_continuous(limits = c(0, 10)) +
  labs(title = "Average Score for Each Type",
       x = "Type",
       y = "Average Score") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


```{r}
average_ratings_rating <- anime_clean %>%
  group_by(Rating) %>%
  summarize(mean_rating = mean(Score))

ggplot(anime_clean, aes(x = Rating, y = as.numeric(Score))) +
  stat_summary(fun = "mean", geom = "col") +
  geom_text(data = average_ratings_rating, aes(label = sprintf("%.2f", mean_rating), y = mean_rating + 0.1), vjust = -0.5) +
  scale_y_continuous(limits = c(0, 10)) +
  labs(title = "Average Score for Each Rating",
       x = "Rating",
       y = "Average Score") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


```{r}
ggplot(anime_clean, aes(x = Year_Premiered, y = Score)) +
  geom_point(stat = "summary", fun = mean, color = "blue") +
  labs(title = "Average Score Over Time",
       x = "Year Premiered",
       y = "Average Score") +
  theme_minimal()
```

Part 4: Modelling

```{r}
model_data <- anime_clean %>%
  select(-c(5:34))

model_data
```

```{r}
print(write_csv(model_data, "model_data.csv"))
```
From here, we can now begin constructing our model. We will first use spectral analysis to find the number of clusters, and then use this value to perform k-means. 

We first perform a spectral analysis of the continuous type data. 
```{r}
model_data_cts = subset(model_data, select = c(Name, Score))
cts_dist_matrix = as.matrix(dist(model_data_cts))
cts_dist_matrix = cts_dist_matrix / max(cts_dist_matrix) # Normalize between 0 and 1

```
Next we perform a spectral analysis of the categorical type data.
```{r}
install.packages("cultevo")
library(cultevo)
model_data_cat = subset(model_data, select = -c(MAL_ID, Score, English.name))
model_data_cat 

cat_hamming_matrix = hammingdists(model_data_cat)
str(cat_hamming_matrix)
```
We from here now construct the dissimilarity matrix $J$ and then compute the affinity matrix $A$ and Laplacian matrix $L$. From there, we compute the eigenvalues and see how many are close to 0 to determine the number of clusters to be used for k-means. 
```{r}
w = 0.5 # tuning parameter
J = (1-w) * cts_dist_matrix + w * cat_hamming_matrix

d = 4 # tuning parameter
A = exp(-(J %*% J)/(2 * d^2))

D = diag(rowSums(A)) 

L = D - A
L_ev = eigen(L)$values
```
And now we